% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[tikz,border=20pt]{cv-style}        
\usepackage{textgreek}
\usepackage{fontspec}
\setmainfont{Scala Pro}[Numbers={Proportional,Lining}]
\setsansfont[Numbers={Proportional,Lining}]{Scala Sans OT}
\newfontfamily{\lighty}{Scala Sans OT Light}
\newcommand{\italica}[1]{%
	{\color{gray} \textit{#1}}%
}
%\usepackage{relsize}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{arev}
%\usepackage{fdsymbol}
\pagestyle{fancy}
\usepackage[object=vectorian]{pgfornament}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
\rfoot{\sffamily Page \thepage{}  of \pageref{LastPage}}
%\usepackage{pifont}
%\DeclareFontFamily{U}{WebOMintsGD}{}
%\DeclareFontShape{U}{WebOMintsGD}{m}{n}{<-> WebOMintsGD}{}
%\usepackage{skak}

% \sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

%\documentclass[tikz, border=20pt]{standalone}
\usetikzlibrary{decorations, decorations.text,}

\begin{document}

\header{Paul Nicola }{Danese}           % Your name
% \lastupdated
%---------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%-----------------------------------------------------------------------

\begin{aside}
%
\section{Contact}
93 Lincoln Drive
Glastonbury, CT USA 
06033-3066
~
+1.860.368.0332
~
\href{mailto:pdanese@goodwin.edu}{pdanese@goodwin.edu}
\href{mailto:pdanese@fdable.com}{pdanese@fdable.com}
%
%
\end{aside}


%--------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%--------------------------------------------------------------------------------

\section{Work History}

\begin{entrylist}
%------------------------------------------------
% GOODWIN
%-------------------------------------------------
\simpleentryheader{2011\textendash}{\href{www.goodwin.edu}{Goodwin University}, School of Nursing \& Health Professions}
\simpleentry{2014\textendash}{Associate Professor}
\simpleentry{2012\textendash 2014}{Assistant Professor}
\simpleentry{2011\textendash 2012}{Adjunct Instructor}
\simpleentry{}{}


  
%------------------------------------------------
% CCC Capital
%-------------------------------------------------
\simpleentryheader{2011\textendash 2019}
  {\href{www.capitalcc.edu}{Capital Community College}, Department of Science \& Mathematics}
\simpleentry{}{Adjunct Instructor}
\simpleentry{}{}
  
  
  
%------------------------------------------------
% EASTERN CT
%-------------------------------------------------
\simpleentryheader{2011\textendash 2012}
  {\href{http://www.easternct.edu/biology/}{Eastern Connecticut State University}, Department of Biology}
\simpleentry{}{Adjunct Instructor}
\simpleentry{}{}
  
  
  
%------------------------------------------------
% FDAble
%------------------------------------------------
\simpleentryheader{2009\textendash}{\href{www.fdable.com}{FDAble}}
\simpleentry{}{Founder}
\simpleentry{}{}



%------------------------------------------------
% RIB-X
%------------------------------------------------
\simpleentryheader{2002\textendash 2009}
  {\href{https://melinta.com/}{Melinta Therapeutics} (formerly Rib-X Pharmaceuticals)}
\simpleentry{2005\textendash 2009}
  {Research Scientist II}
\simpleentry{2002\textendash 2005}
  {Research Scientist}
\simpleentry{}{}
  


%------------------------------------------------
% MICROBIA
%------------------------------------------------
\simpleentryheader{2000\textendash 2002}
  {\href{www.ironwoodpharma.com}{Ironwood Pharmaceuticals} (formerly Microbia)}
\simpleentry{{2002}}{Program Manager}
\simpleentry{{2000\textendash 2002}}{Team Leader}
\simpleentry{2000}{Senior Scientist}
\simpleentry{}{}



%------------------------------------------------
% HARVARD MED
%------------------------------------------------
\simpleentryheader{1999\textendash 2000}
  {\href{http://micro.med.harvard.edu/}{Harvard Medical School}, Department of Microbiology \& Molecular Genetics}
\simpleentry{}{Postdoctoral Fellow}
\simpleentry{}{}



%------------------------------------------------
% HARVARD MCB
%------------------------------------------------
\simpleentryheader{1996\textendash 1999}
  {\href{https://www.mcb.harvard.edu/}{Harvard University}, Department of Molecular \& Cellular Biology}
\simpleentry{}{Postdoctoral Fellow}
\simpleentry{}{}


\end{entrylist}
%------------------------------------------------
% END OF WORK HISTORY
% END OF WORK HISTORY
% END OF WORK HISTORY
%------------------------------------------------


%---------------------------------------------------------------------
%	EDUCATION SECTION
%	EDUCATION SECTION
%	EDUCATION SECTION
%	EDUCATION SECTION
%---------------------------------------------------------------------
\section{Education}

\begin{entrylist}

%---------------------------------------------------------------------
%	PRINCETON
%---------------------------------------------------------------------
\simpleentryheader{1990\textendash 1996}{\coloredhref{orange}{https://molbio.princeton.edu/}{Princeton University}, Department of Molecular Biology}
\simpleentry{1996}{Doctor of Philosophy. Thesis Advisor: Thomas J. Silhavy}
\simpleentry{1992}{Master of Arts. Thesis Advisor: Thomas J. Silhavy}
\simpleentry{}{}


%---------------------------------------------------------------------
%	UMASS
%---------------------------------------------------------------------
\simpleentryheader{1986\textendash 1990}
{\coloredhref{orange}{https://www.umass.edu/biochem/}{University of Massachusetts, Amherst}, Department of Biochemistry}
\simpleentry{1990}{Bachelor of Science. Thesis Advisor: Thomas L. Mason}
\simpleentry{}{}

%------------------------------------------------
\end{entrylist}
%---------------------------------------------------------------------
%	END EDUCATION SECTION
%	END EDUCATION SECTION
%	END EDUCATION SECTION
%---------------------------------------------------------------------



\pagebreak{}
\header{Danese}{}           % Your name
%---------------------------------------------------------------------
%	TEACHING EXPERIENCE
%	TEACHING EXPERIENCE
%	TEACHING EXPERIENCE
%---------------------------------------------------------------------

\section{Teaching Experience}
\begin{entrylist}

%---------------------------------------------------------------------
%	GOODWIN TEACHING
%---------------------------------------------------------------------
\simpleentryheader{2011\textendash}{Goodwin College}
\simpleentry{2018\textendash}{Chemistry 110 (General Chemistry I)}
\simpleentry{2018\textendash}{Chemistry 111 (General Chemistry II)}
\simpleentry{2016}{Chemistry 101 (Introductory Chemistry), hybrid}
\simpleentry{2013\textendash}{Chemistry 101 (Introductory Chemistry), on-line}
\simpleentry{2011\textendash}{Chemistry 101 (Introductory Chemistry)}
\simpleentry{}{}


%-----------------------------------------------------------------
%	CCC TEACHING
%---------------------------------------------------------------------
\simpleentryheader{2011\textendash 2019}{Capital Community College}
\simpleentry{2016\textendash 2019}{Chemistry 122 (General Chemistry II)}
\simpleentry{2016\textendash 2019}{Chemistry 121 (General Chemistry I}
\simpleentry{2014\textendash 2016}{Biology 235 (Microbiology)}
\simpleentry{2012\textendash 2015}{Chemistry 111 (Concepts in Chemistry)}
\simpleentry{2012\textendash 2015}{Biology 121 (General Biology)}
\simpleentry{2011\textendash 2012}{Biology 105 (Introductory Biology)}
\simpleentry{}{}


%-----------------------------------------------------------------
%	EASTERN CT TEACHING
%---------------------------------------------------------------------
\simpleentryheader{2011\textendash 2012}{Eastern Connecticut State University}
\simpleentry{}{Genetics \& Society Laboratory}
\simpleentry{}{}


%-----------------------------------------------------------------
%	COURSERA TEACHING
%------------------------------------------------------------
\simpleentryheader{2014\textendash 2015}{\coloredhref{aquamarine}{https://www.coursera.org/}{Coursera}}
\simpleentry{2014}{Invited teaching assistant for \coloredhref{darkeraqua}{https://www.coursera.org/learn/datavisualization}{Data Visualization}}
\simpleentry{2014}{Invited teaching assistant for \coloredhref{darkeraqua}{https://www.coursera.org/learn/statistical-inference}{Statistical Inference}}
\simpleentry{2014}{Invited teaching assistant for \coloredhref{darkeraqua}{https://www.coursera.org/learn/practical-machine-learning}{Practical Machine Learning}}
\simpleentry{}{}



%-----------------------------------------------------------------
%	HMS TEACHING
%------------------------------------------------------------
\simpleentryheader{1999\textendash 2000 \hfill}{Harvard Medical School}
\simpleentry{2000}{Guest Lecturer, Graduate course in Molecular Genetics}
\simpleentry{1999}{Mentor for one graduate rotation student}
\simpleentry{1999}{Teaching Assistant, Medical Microbiology Laboratory}
\simpleentry{}{}


%-----------------------------------------------------------------
%	HARVARD MCB TEACHING
%------------------------------------------------------------
\simpleentryheader{1997\textendash 1998}{Harvard University}
\simpleentry{1998}{Teaching Assistant, Introductory Biochemistry}
\simpleentry{1997}{Mentor for two undergraduate research assistants}
\simpleentry{}{}


%-----------------------------------------------------------------
%	PRINCETON TEACHING
%------------------------------------------------------------
\simpleentryheader{1991\textendash 1996}{Princeton University}
\simpleentry{1992\textendash 1996}{Mentor for two undergraduates conducting thesis research}
\simpleentry{1992\textendash 1996}{Mentor for three graduate rotation students}
\simpleentry{1991}{Teaching Assistant for MOL345, (Introductory Biochemistry)}
\simpleentry{1991}{Teaching Assistant for MOL212, (Introductory Molecular Biology)}
\simpleentry{}{}


\end{entrylist}
%-----------------------------------------------------------------
%	END TEACHING
%	END TEACHING
%	END TEACHING
%------------------------------------------------------------


%----------------------------------------
% AWARDS
%----------------------------------------

\section{Awards}

\begin{entrylist}

%----------------------------------------
% DAMON RUNYON
%----------------------------------------
\simpleentryheader{1997\textendash 2000}{\coloredhref{purple}{https://www.damonrunyon.org/}{Cancer Research Fund of the Damon Runyon\textendash Walter Winchell Foundation}}
\simpleentry{}{Postdoctoral Fellowship}
\simpleentry{}{}



%----------------------------------------
% PRINCETON GRAD SCHOLARSHIP
%----------------------------------------
\simpleentryheader{1990\textendash 1991}{Princeton University}
\simpleentry{}{Graduate Scholarship Award}
\simpleentry{}{}


%----------------------------------------
% UMASS AWARDS
%----------------------------------------
\simpleentryheader{1986\textendash 1990}{University of Massachusetts, Amherst}
\simpleentry{1990}{Inducted, \textPhi BK Honor Society}
\simpleentry{1990}{Henry Little Award}
\simpleentry{}{\italica{Awarded to highest-ranked senior in the Department of Biochemistry}}
\simpleentry{1986\textendash 1990}{Chancellor's Talent Award Scholarship}
\simpleentry{}{\italica{Tuition waiver based on academic performance}}
\simpleentry{}{}


\end{entrylist}


\pagebreak{}
\header{Danese}{}           % Your name
%------------------------------------------------------------------------
%	PUBLICATIONS
%	PUBLICATIONS
%	PUBLICATIONS
%----------------------------------------------------------------------
\section{Peer-Reviewed Research}

\begin{entrylist}
\simpleentry{2021}{Danese, PN. Search and Analysis of the Food and Drug Administration’s (FDA) Adverse Event Reporting System (FAERS). in \textbf{O'Donnell's Drug Injury} 5th edition. James T O’Donnell, editor.}
\simpleentry{}{}


\simpleentry{2017}{Tayek, JA, Danese PNN, and Smith MS. Safety of Degludec versus Glargine in Type 2 Diabetes. \italica{New England Journal of Medicine}, \textbf{377}: 1994\textendash{}1996.}
\simpleentry{}{}

\simpleentry{2016}{Danese, PN. Search and Analysis of the Food and Drug Administration’s (FDA) Adverse Event Reporting System (FAERS). in \textbf{O'Donnell's Drug Injury} 4th edition. James T O’Donnell, editor.}
\simpleentry{}{}


\simpleentry{2014}{O’Donnell, JT, Marks, DH, Danese P, and JJ O’Donnell. Drug-Induced Liver Disease: Primer for the Primary Care Physician. \italica{Disease-a-Month}, \textbf{60}: 55\textendash{}104.}
\simpleentry{}{}

\simpleentry{2012}{Danese, PN. Search and Analysis of the Food and Drug Administration’s Adverse Event Reporting System. p 195\textendash{}204, in \textbf{Drug Injury: Liability Analysis \& Prevention} 3rd edition. James T. O’Donnell, editor.}
\simpleentry{}{}

\simpleentry{2012}{Somberg, JC, McEwen, P, Basu, S, Danese, PN, and J Molnar. Medical Device Recalls in the US.  \italica{Circulation}: \textbf{126}: A11403.}
\simpleentry{}{}

\simpleentry{2009}{Pratt, LA and P Danese. More Eyeballs on AERS. \italica{Nature Biotechnology}, \textbf{27}: 601\textendash{}602.}
\simpleentry{}{}

\simpleentry{2008}{Lawrence, L, Danese P, DeVito, J, Franceschi, F, and J Sutcliffe. \italica{In vitro} activities of the R\textchi-01 oxazolidinones against hospital and community pathogens. \italica{Antimicrobial Agents and Chemotherapy}, \textbf{52}: 1653\textendash{}1662.}
\simpleentry{}{}

\simpleentry{2002}{Danese, PN. Antibiofilm approaches: prevention of catheter colonization. \italica{Chemistry and Biology}, \textbf{9}: 873\textendash{}880.}
\simpleentry{}{}

\simpleentry{2001}{Danese, PN, Pratt, LA, and R Kolter. Biofilm formation as a developmental process. \italica{Methods in Enzymology}, \textbf{336}: 19\textendash{}26.}
\simpleentry{}{}


\simpleentry{2000}{Danese, PN, Pratt, LA, Dove, S, and R Kolter. The outer-membrane protein, Ag43, mediates cell-to-cell interactions within \italica{E. coli} biofilms. \italica{Molecular Microbiology}, \textbf{37}: 424\textendash{}432.}
\simpleentry{}{}

\simpleentry{2000}{Danese, PN, Pratt, LA, and R Kolter. Exopolysaccharide production is required for development \italica{Escherichia coli} K-12 biofilm architecture. \italica{Journal of Bacteriology}, \textbf{182}: 3593\textendash{}3596.}
\simpleentry{}{}

\simpleentry{1999}{Samuel, ADT, Pitta TP, Ryu, WS, Danese PN, Leung ECW, and HC Berg. 1999. Flagellar determinants of bacterial sensitivity to \textchi-phage. \italica{Proceedings of the National Academy of Sciences, USA}, \textbf{96}: 9863\textendash{}9866.}
\simpleentry{}{}

\simpleentry{1998}{Danese, PN, Oliver, GR, Barr, K, Bowman GD, Rick, PD, and TJ Silhavy. Accumulation of the Enterobacterial Common Antigen Lipid II Biosynthetic Intermediate Stimulates \italica{degP} Transcription in \italica{Escherichia coli}. \italica{Journal of Bacteriology}, \textbf{180}: 5875\textendash{}5884.}
\simpleentry{}{}

\simpleentry{1998}{Danese, PN, and TJ Silhavy. Targeting and Assembly of Periplasmic and Outer-membrane Proteins in \italica{Escherichia coli}. \italica{Annual Review of Genetics}, \textbf{32}: 59\textendash{}94.}
\simpleentry{}{}

\simpleentry{1998}{Danese, PN, and TJ Silhavy. CpxP, a Stress-combative Member of the Cpx Regulon in \italica{Escherichia coli}. \italica{Journal of Bacteriology}, \textbf{180}: 831\textendash{}839.}
\simpleentry{}{}


\end{entrylist}

\pagebreak{}
\header{Danese}{}           % Your name
\section{Peer-Reviewed Research Continued}

\begin{entrylist}

\simpleentry{1997}{Jones, CH, Danese, PN, Pinkner, JS, Silhavy TJ, and SJ Hultgren. The Chaperone-assisted Membrane Release and Folding Pathway is Sensed by Two Signal Transduction Systems. \italica{EMBO Journal}, \textbf{16}: 6394\textendash{}6406.}
\simpleentry{}{}

\simpleentry{1997}{Danese, PN and TJ Silhavy. 1997. The \textsigma-E and the Cpx Signal Transduction Systems Control the Synthesis of Periplasmic Protein-Folding Enzymes in \italica{Escherichia coli}. \italica{Genes \& Development}, \textbf{11}: 1183\textendash{}1193.}
\simpleentry{}{}

\simpleentry{1995}{Danese, PN, Snyder, WB, Cosma CL, Davis LJB, and TJ Silhavy. The Cpx Two-component Signal Transduction Pathway of \italica{Escherichia coli} Regulates Transcription of the Gene Specifying the Stress-inducible Periplasmic Protease, DegP. \italica{Genes \& Development}, \textbf{9}: 387\textendash{}398.}
\simpleentry{}{}

\simpleentry{1995}{Danese, PN, Murphy, CK, and TJ Silhavy. Multicopy Suppression of Cold-sensitive \italica{sec} Mutations in \italica{Escherichia coli}. \italica{Journal of Bacteriology}, \textbf{177}: 4969\textendash{}4973.}
\simpleentry{}{}

\simpleentry{1995}{Snyder, WB, Davis, LBJ, Danese PN, Cosma CL, and TJ Silhavy. Overproduction of NlpE, a New Outer-membrane Lipoprotein, Suppresses the Toxicity of Periplasmic LacZ by Activation of the Cpx Signal Transduction Pathway. \italica{Journal of Bacteriology}, \textbf{177}: 4216\textendash{}4223.}
\simpleentry{}{}

\simpleentry{1995}{Cosma, CL, Danese PN, Carlson, JH, Silhavy TJ, and WB Snyder. Activation of the Cpx Two-component Signal Transduction Pathway in \italica{Escherichia coli} Suppresses Envelope Associated Stresses. \italica{Molecular Microbiology}, \textbf{18}: 491\textendash{}505.}
\simpleentry{}{}

\simpleentry{1993}{Leonhardt, SA, Fearon, K, Danese, PN, and TL Mason. 1993. \italica{HSP78} Encodes a Yeast Mitochondrial Heat Shock Protein in the Clp Family of ATP-dependent Proteases. \italica{Molecular and Cellular Biology}, \textbf{13}: 6304\textendash{}6314.}
\simpleentry{}{}
\end{entrylist}


%---------------------------------------------------------------
%	SKILLS
%	SKILLS
%	SKILLS
%------------------------------------------------------------------------
\section{Computer Skills}

\begin{entrylist}
%------------------------------------------------
\simpleentryheader{}{General Purpose Programming Languages}
\simpleentry{}{Python, Java,  Ruby, VBScript}
\simpleentry{}{}

\simpleentryheader{}{Machine Learning / Scientific Programming}
\simpleentry{}{ChemAxon Marvin, OpenBabel, R, Scikit-Learn, SciPy}
\simpleentry{}{}

\simpleentryheader{}{Relational Databases}
\simpleentry{}{MySQL, Oracle, SQLite}
\simpleentry{}{}

\simpleentryheader{}{Office Productivity \& Publishing}
\simpleentry{}{\textcolor{red}{☛} \LaTeX, Microsoft Office, PowerBI, VBA}
\simpleentry{}{}

\simpleentryheader{}{Web Development}
\simpleentry{}{CSS, HTML, Javascript, Lucene,  Ruby on Rails, Solr}
\simpleentry{}{}





%------------------------------------------------
%------------------------------------------------

\end{entrylist}
%--------------------------------------------------------------------
%	Hobby SECTION
%	Hobby SECTION
%	Hobby SECTION
%-----------------------------------------------------------
\section{Hobbies}
 
\begin{tikzpicture}[remember picture, overlay]
\tikzset{curveinscope/.style={every path/.style={text=red}}}
   \path [decorate,decoration={text along path,
        text={  
            |\color{blue}\raisebox{-0.0em}{☛}| 
            |\color{gray}|Chess %
            |\textperiodcentered| %
            ||%
            |\color{gray}|Digital Photography % 
            |\textperiodcentered| %
            ||%
            |\color{gray}|Digital Typography %
            |\textperiodcentered| %
            ||%
            |\color{gray}|Piano % 
            |\color{blue}|☚
  }}]
        (3.1,1) arc [start angle=-146.5,end angle=80,radius=4.79];
    \end{tikzpicture}


% \begin{entrylist}
% \simpleentry{}{Chess}
% \simpleentry{}{Digital Photography}

% %------------------------------------------------
% %------------------------------------------------

% \end{entrylist}



\end{document}